The "dark-side" of phylogenetic comparative methods

### 2014-05-22 Manuscript/dark.tex
Initial commit of bibliography files

\runninghead{The dark-side of PCMs}
\keywords{some words}

\begin{document}
%\pagestyle{empty}
\modulolinenumbers[1]   % Line numbering on every line

@@

\begin{abstract}
\raggedright
\singlespacing
An abstract abstract
\end{abstract}

\newpage
\raggedright
\doublespacing
\section{Introduction}

@@

@@

\section{Acknowledgments}

NC is supported by Marie Curie CIG grant (proposal no: )

%\bibliographystyle{systbiol}
%\bibliography{darkside.bib}

>>>>

\runninghead{The dark-side of PCMs} % "Point of view" for Syst Biol
\keywords{some words}

%%%
% From Syst Biol template
\linespread{1.66}
\raggedright
\setlength{\parindent}{0.5in}

\pagestyle{empty}

\renewcommand{\section}[1]{%
\bigskip
\begin{center}
\begin{Large}
\normalfont\scshape #1
\medskip
\end{Large}
\end{center}}

\renewcommand{\subsection}[1]{%
\bigskip
\begin{center}
\begin{large}
\normalfont\itshape #1
\end{large}
\end{center}}

\renewcommand{\subsubsection}[1]{%
\vspace{2ex}
\noindent
\textit{#1.}---}

\renewcommand{\tableofcontents}{}

\bibpunct{(}{)}{;}{a}{}{,}  % this is a citation format command for natbib

% Ignoring their title page setup as I like Rich's template better :)

%%%%%

\begin{document}
\modulolinenumbers[1]   % Line numbering on every line

@@

\section{abstract}
An abstract abstract % If "Point of View" there's no abstract

\newpage
\raggedright
\doublespacing
%\section{Introduction} % No intro heading for Syst biol

@@

We extracted yearly citation counts from the Web of Science on 22nd May 2013 for the following papers: \citet{boettiger2012your,blomberg2012independent,diaz1996testing,felsenstein1988phylogenies,felsenstein1985phylogenies,freckleton2009seven,freckleton2000phylogenetic,freckleton2002phylogenetic,freckleton2006detecting,grafen1989phylogenetic,garland1992procedures,hansen1997stabilizing,hansen1996translating,hansen2005assessing,jones1997optimum,garland2000using,garland1992rate,martins1997phylogenies,nee1994extinction,price1997correlated,rohle2006comment,ricklefs1996applications,rohlf2001comparative,schluter1997likelihood,westoby1995misinterpreting,westoby1995further}. We also obtained citation counts for \citet{harvey1991comparative} using Google Scholar, as Web of Science does not provide citation counts for books.

@@

\section{Acknowledgments}
NC is supported by The European Commission CORDIS Seventh Framework Programme (FP7) Marie Curie CIG grant, proposal number: 321696.

\bibliographystyle{sysbio}
\bibliography{darkside}
